% Acknowledgments and Presentations

\section*{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}

This section is dedicated to acknowledging the institutions and individuals who made this project possible.

\subsection*{University Presentation}
\addcontentsline{toc}{subsection}{University Presentation}

\textbf{Academic Institution:} University Name\\
\textbf{Faculty:} Faculty of Engineering and Technology\\
\textbf{Department:} Computer Science and Information Technology\\
\textbf{Degree Program:} Bachelor of Engineering in Software Engineering\\
\textbf{Academic Year:} 2024-2025\\
\textbf{Academic Supervisor:} Professor Name\\
\textbf{Academic Supervisor Title:} Professor of Software Engineering\\

\vspace{1cm}

\textbf{Project Details:}
\begin{itemize}
\item \textbf{Project Title:} ErrorZen: Intelligent Platform for Automated Error Management
\item \textbf{Project Type:} Final Year Project (Projet de Fin d'Études)
\item \textbf{Project Duration:} 6 months (March 2024 - September 2024)
\item \textbf{Project Category:} Software Engineering \& Artificial Intelligence
\end{itemize}

\subsection*{Internship Company Presentation}
\addcontentsline{toc}{subsection}{Company Presentation}

\textbf{Company Name:} Company Name\\
\textbf{Industry:} Technology Solutions and Software Development\\
\textbf{Company Size:} Enterprise-level technology company\\
\textbf{Location:} City, Country\\
\textbf{Website:} www.company-website.com\\

\vspace{0.5cm}

\textbf{Internship Details:}
\begin{itemize}
\item \textbf{Position:} Software Development Intern
\item \textbf{Department:} Research and Development
\item \textbf{Company Supervisor:} Supervisor Name
\item \textbf{Supervisor Title:} Senior Software Engineer / Technical Lead
\item \textbf{Internship Duration:} 6 months
\item \textbf{Start Date:} Date
\item \textbf{End Date:} Date
\end{itemize}

\vspace{0.5cm}

\textbf{Company Mission:}
The company specializes in developing innovative software solutions that leverage artificial intelligence and machine learning to solve complex business problems. The organization focuses on creating scalable, robust applications that enhance operational efficiency and provide intelligent automation capabilities.

\subsection*{Gratitude and Acknowledgments}
\addcontentsline{toc}{subsection}{Gratitude}

I would like to express my sincere gratitude to all the individuals and institutions who contributed to the successful completion of this project:

\textbf{Academic Acknowledgments:}
\begin{itemize}
\item Professor Name, my academic supervisor, for providing invaluable guidance, technical expertise, and continuous support throughout the project development process.
\item The Faculty of Engineering and Technology for providing the academic framework and resources necessary for this research.
\item My fellow students and colleagues who provided feedback and collaboration during the development phases.
\end{itemize}

\textbf{Professional Acknowledgments:}
\begin{itemize}
\item Supervisor Name, my company supervisor, for mentoring me through the practical implementation aspects and providing industry insights.
\item The development team at Company Name for their technical guidance and collaborative support.
\item The company management for providing access to development resources, tools, and real-world testing environments.
\end{itemize}

\textbf{Technical Acknowledgments:}
\begin{itemize}
\item The open-source community for providing the foundational technologies used in this project.
\item DeepSeek AI for providing access to their advanced language models that powered the intelligent error analysis features.
\item The creators and maintainers of Go, Vue.js, PostgreSQL, and other technologies that formed the technical foundation of ErrorZen.
\end{itemize}

\textbf{Personal Acknowledgments:}
\begin{itemize}
\item My family for their unwavering support and encouragement throughout my academic journey.
\item Friends and peers who provided motivation and valuable feedback during the project development.
\item Everyone who participated in testing and validating the ErrorZen platform during its development phases.
\end{itemize}

This project represents the culmination of my undergraduate studies and would not have been possible without the collective support, guidance, and expertise of all the mentioned individuals and institutions. Their contributions have been instrumental in both my personal growth and the successful realization of the ErrorZen platform.

\newpage