% Bibliography Section

\section*{Bibliography}
\addcontentsline{toc}{section}{Bibliography}

This section contains references to all external sources, technologies, frameworks, and research materials that were consulted during the development of the ErrorZen project.

\subsection*{Technical Documentation and Official Sources}

\begin{enumerate}
\item \textbf{Go Programming Language Documentation}\\
The Go Team. \textit{The Go Programming Language Documentation}. Google, 2024.\\
Available at: \url{https://golang.org/doc/}\\
Accessed: September 2024.

\item \textbf{Vue.js Framework Documentation}\\
Evan You and Contributors. \textit{Vue.js - The Progressive JavaScript Framework}. Vue.js Team, 2024.\\
Available at: \url{https://vuejs.org/guide/}\\
Accessed: September 2024.

\item \textbf{PostgreSQL Database Documentation}\\
PostgreSQL Global Development Group. \textit{PostgreSQL 15 Documentation}. PostgreSQL, 2024.\\
Available at: \url{https://www.postgresql.org/docs/15/}\\
Accessed: September 2024.

\item \textbf{Gin Web Framework Documentation}\\
Gin Contributors. \textit{Gin Web Framework for Go}. GitHub, 2024.\\
Available at: \url{https://gin-gonic.com/docs/}\\
Accessed: September 2024.

\item \textbf{Docker Documentation}\\
Docker Inc. \textit{Docker Official Documentation}. Docker, 2024.\\
Available at: \url{https://docs.docker.com/}\\
Accessed: September 2024.

\item \textbf{GitHub Actions Documentation}\\
GitHub Inc. \textit{GitHub Actions Documentation}. GitHub, 2024.\\
Available at: \url{https://docs.github.com/en/actions}\\
Accessed: September 2024.

\item \textbf{WebSocket Protocol Specification}\\
IETF. \textit{RFC 6455 - The WebSocket Protocol}. Internet Engineering Task Force, 2011.\\
Available at: \url{https://tools.ietf.org/html/rfc6455}\\
Accessed: September 2024.

\item \textbf{JSON Web Tokens (JWT) Specification}\\
IETF. \textit{RFC 7519 - JSON Web Token (JWT)}. Internet Engineering Task Force, 2015.\\
Available at: \url{https://tools.ietf.org/html/rfc7519}\\
Accessed: September 2024.

\item \textbf{gRPC Documentation}\\
Google Inc. \textit{gRPC - A high performance, open source universal RPC framework}. Google, 2024.\\
Available at: \url{https://grpc.io/docs/}\\
Accessed: September 2024.

\item \textbf{Protocol Buffers Documentation}\\
Google Inc. \textit{Protocol Buffers Developer Guide}. Google, 2024.\\
Available at: \url{https://developers.google.com/protocol-buffers}\\
Accessed: September 2024.
\end{enumerate}

\subsection*{Error Monitoring and Management Research}

\begin{enumerate}
\setcounter{enumi}{10}
\item \textbf{Sentry Error Tracking Platform}\\
Functional Software Inc. \textit{Sentry - Application Performance Monitoring \& Error Tracking Software}. Sentry, 2024.\\
Available at: \url{https://sentry.io/}\\
Accessed: September 2024.

\item \textbf{Rollbar Error Monitoring}\\
Rollbar Inc. \textit{Rollbar - Continuous Code Improvement Platform}. Rollbar, 2024.\\
Available at: \url{https://rollbar.com/}\\
Accessed: September 2024.

\item \textbf{Bugsnag Error Monitoring}\\
SmartBear Software. \textit{Bugsnag - Application Stability Management}. Bugsnag, 2024.\\
Available at: \url{https://www.bugsnag.com/}\\
Accessed: September 2024.

\item \textbf{Datadog APM and Error Tracking}\\
Datadog Inc. \textit{Datadog - Application Performance Monitoring}. Datadog, 2024.\\
Available at: \url{https://www.datadoghq.com/product/apm/}\\
Accessed: September 2024.

\item \textbf{New Relic Application Monitoring}\\
New Relic Inc. \textit{New Relic - Full-Stack Observability Platform}. New Relic, 2024.\\
Available at: \url{https://newrelic.com/}\\
Accessed: September 2024.

\item \textbf{Application Performance Monitoring Best Practices}\\
Gartner Inc. \textit{Magic Quadrant for Application Performance Monitoring and Observability}. Gartner, 2023.\\
Available at: \url{https://www.gartner.com/en/documents/4020902}\\
Accessed: September 2024.
\end{enumerate}

\subsection*{Artificial Intelligence and Machine Learning}

\begin{enumerate}
\setcounter{enumi}{16}
\item \textbf{DeepSeek AI Platform}\\
DeepSeek AI. \textit{DeepSeek - Advanced AI Language Models}. DeepSeek, 2024.\\
Available at: \url{https://www.deepseek.com/}\\
Accessed: September 2024.

\item \textbf{OpenAI GPT Documentation}\\
OpenAI. \textit{GPT Models and API Documentation}. OpenAI, 2024.\\
Available at: \url{https://platform.openai.com/docs/}\\
Accessed: September 2024.

\item \textbf{Natural Language Processing for Error Classification}\\
Manning, Christopher D., and Hinrich Schütze. \textit{Foundations of Statistical Natural Language Processing}. MIT Press, 1999.

\item \textbf{Machine Learning for Software Engineering}\\
Menzies, Tim, et al. \textit{Perspectives on Data Science for Software Engineering}. Morgan Kaufmann, 2016.

\item \textbf{Automated Bug Triaging Using Machine Learning}\\
Anvik, John, et al. "Who should fix this bug?" \textit{Proceedings of the 28th International Conference on Software Engineering}. ACM, 2006.
\end{enumerate}

\subsection*{Software Development Methodologies}

\begin{enumerate}
\setcounter{enumi}{21}
\item \textbf{Agile Software Development}\\
Beck, Kent, et al. \textit{Manifesto for Agile Software Development}. Agile Alliance, 2001.\\
Available at: \url{https://agilemanifesto.org/}\\
Accessed: September 2024.

\item \textbf{Scrum Framework Guide}\\
Schwaber, Ken, and Jeff Sutherland. \textit{The Scrum Guide - The Definitive Guide to Scrum}. Scrum.org, 2020.\\
Available at: \url{https://scrumguides.org/}\\
Accessed: September 2024.

\item \textbf{DevOps Practices and CI/CD}\\
Kim, Gene, et al. \textit{The DevOps Handbook: How to Create World-Class Agility, Reliability, \& Security in Technology Organizations}. IT Revolution Press, 2016.

\item \textbf{Continuous Integration and Continuous Deployment}\\
Fowler, Martin. \textit{Continuous Integration}. Martin Fowler's Blog, 2006.\\
Available at: \url{https://martinfowler.com/articles/continuousIntegration.html}\\
Accessed: September 2024.
\end{enumerate}

\subsection*{Web Development and API Design}

\begin{enumerate}
\setcounter{enumi}{25}
\item \textbf{RESTful API Design Principles}\\
Fielding, Roy Thomas. \textit{Architectural Styles and the Design of Network-based Software Architectures}. Doctoral dissertation, University of California, Irvine, 2000.

\item \textbf{Modern Web Application Architecture}\\
Gamma, Erich, et al. \textit{Design Patterns: Elements of Reusable Object-Oriented Software}. Addison-Wesley, 1994.

\item \textbf{Microservices Architecture Patterns}\\
Newman, Sam. \textit{Building Microservices: Designing Fine-Grained Systems}. O'Reilly Media, 2015.

\item \textbf{Real-time Web Applications}\\
W3C. \textit{WebSocket API Specification}. World Wide Web Consortium, 2024.\\
Available at: \url{https://www.w3.org/TR/websockets/}\\
Accessed: September 2024.
\end{enumerate}

\subsection*{Database Design and Management}

\begin{enumerate}
\setcounter{enumi}{30}
\item \textbf{Database Design Principles}\\
Codd, Edgar F. "A Relational Model of Data for Large Shared Data Banks." \textit{Communications of the ACM}, vol. 13, no. 6, 1970, pp. 377-387.

\item \textbf{NoSQL Database Concepts}\\
Redmond, Eric, and Jim R. Wilson. \textit{Seven Databases in Seven Weeks: A Guide to Modern Databases and the NoSQL Movement}. Pragmatic Bookshelf, 2012.

\item \textbf{Database Performance Optimization}\\
Kamps, Jörg, and Robert Marx. \textit{SQL Performance Explained}. Markus Winand, 2012.

\item \textbf{ACID Properties in Database Systems}\\
Gray, Jim, and Andreas Reuter. \textit{Transaction Processing: Concepts and Techniques}. Morgan Kaufmann, 1993.
\end{enumerate}

\subsection*{Security and Authentication}

\begin{enumerate}
\setcounter{enumi}{34}
\item \textbf{OAuth 2.0 Authorization Framework}\\
IETF. \textit{RFC 6749 - The OAuth 2.0 Authorization Framework}. Internet Engineering Task Force, 2012.\\
Available at: \url{https://tools.ietf.org/html/rfc6749}\\
Accessed: September 2024.

\item \textbf{Web Application Security}\\
OWASP Foundation. \textit{OWASP Top Ten Web Application Security Risks}. OWASP, 2021.\\
Available at: \url{https://owasp.org/www-project-top-ten/}\\
Accessed: September 2024.

\item \textbf{Cryptographic Hash Functions}\\
NIST. \textit{FIPS PUB 180-4 - Secure Hash Standard (SHS)}. National Institute of Standards and Technology, 2015.\\
Available at: \url{https://nvlpubs.nist.gov/nistpubs/FIPS/NIST.FIPS.180-4.pdf}\\
Accessed: September 2024.

\item \textbf{Password Security Best Practices}\\
Burr, William E., et al. \textit{NIST Special Publication 800-63B - Authentication and Lifecycle Management}. NIST, 2017.\\
Available at: \url{https://pages.nist.gov/800-63-3/sp800-63b.html}\\
Accessed: September 2024.
\end{enumerate}

\subsection*{Software Testing and Quality Assurance}

\begin{enumerate}
\setcounter{enumi}{38}
\item \textbf{Software Testing Fundamentals}\\
Myers, Glenford J., et al. \textit{The Art of Software Testing}. 3rd ed., John Wiley \& Sons, 2011.

\item \textbf{Test-Driven Development}\\
Beck, Kent. \textit{Test Driven Development: By Example}. Addison-Wesley Professional, 2002.

\item \textbf{Unit Testing Best Practices}\\
Osherove, Roy. \textit{The Art of Unit Testing: with examples in C\#}. 2nd ed., Manning Publications, 2013.

\item \textbf{Integration Testing Strategies}\\
Fowler, Martin. \textit{TestPyramid}. Martin Fowler's Blog, 2018.\\
Available at: \url{https://martinfowler.com/articles/practical-test-pyramid.html}\\
Accessed: September 2024.
\end{enumerate}

\subsection*{Performance Monitoring and Optimization}

\begin{enumerate}
\setcounter{enumi}{42}
\item \textbf{Application Performance Monitoring}\\
Gregg, Brendan. \textit{Systems Performance: Enterprise and the Cloud}. 2nd ed., Addison-Wesley Professional, 2020.

\item \textbf{Web Performance Optimization}\\
Souders, Steve. \textit{High Performance Web Sites: Essential Knowledge for Front-End Engineers}. O'Reilly Media, 2007.

\item \textbf{Database Performance Tuning}\\
Shasha, Dennis, and Philippe Bonnet. \textit{Database Tuning: Principles, Experiments, and Troubleshooting Techniques}. Morgan Kaufmann, 2002.

\item \textbf{Scalable System Design}\\
Kleppmann, Martin. \textit{Designing Data-Intensive Applications}. O'Reilly Media, 2017.
\end{enumerate}

\subsection*{Project Management and Documentation}

\begin{enumerate}
\setcounter{enumi}{46}
\item \textbf{Software Project Management}\\
Pressman, Roger S., and Bruce R. Maxim. \textit{Software Engineering: A Practitioner's Approach}. 8th ed., McGraw-Hill Education, 2014.

\item \textbf{Technical Documentation Best Practices}\\
Redish, Janice C. \textit{Letting Go of the Words: Writing Web Content that Works}. 2nd ed., Morgan Kaufmann, 2012.

\item \textbf{User Experience Design}\\
Norman, Donald A. \textit{The Design of Everyday Things}. Revised ed., Basic Books, 2013.

\item \textbf{API Documentation Standards}\\
OpenAPI Initiative. \textit{OpenAPI Specification}. Linux Foundation, 2024.\\
Available at: \url{https://swagger.io/specification/}\\
Accessed: September 2024.
\end{enumerate}

\vspace{1cm}

\textbf{Note:} All online resources were accessed and verified during the period of September-October 2024. The information and documentation from these sources were used to inform the design decisions, implementation strategies, and best practices applied in the ErrorZen project development.

\newpage